Clustering Beat-Chroma Patterns in a Large Music Database

### 2010-03-23 Paper/Paper.tex
typo

% Q: Why are there long spaces after "e.g." or "i.e."?
% A: LaTeX interprets a dot and a blank as the end of a sentence. To
%    prevent this, use "e.g.\ " and "i.e.\ " or "e.g.~" and "i.e.~".
\newcommand{\ie}{i.e.~}
\newcommand{\Ie}{I.e.~}
\newcommand{\eg}{e.g.~}
\newcommand{\Eg}{E.g.~}

@@

\subsection{Pattern Creation}
Patterns are defined as a number of beats or bars. In the case of beats,
we simply cut the set of chromas per beat every $N$ beats. In the case
of bars, we gather all beats corresponding to the $N$ bars requested.
The number of chroma vectors we get can vary. We resize the features in the
time axis to a fixed length. Resizing can be argued over, but it should
preserve the main bar characteristics (such as a strong beat at the beginning
or a note change in the middle).

@@

\subsection{Codebook}
Visualizing codewords in a meaningful way is always a challenge, even
if we have only a one or two hundreds of them.  We present $3$ figures
in this section that should help the reader foster his
intuition.

FIXME: fix the labels in the figure (label pitch class on the y axis,
and maybe only beats [0 2 4 6] on the ax axis, add codeword numbers to
title), etc.

The 25 most frequently used codewords in the testing set are shown in
Figure \ref{fig:codes1}.  The codewords primarily consist of sustained
notes and simple chords.  Since they are designed to be key-invariant,
specific notes do not appear.  Instead the first 7 codewords
correspond to a single note sustained across two bars (codeword 1),
perfect fifth (codes 2 and 3) and fourth intervals (codes 4 7), and a
major and minor triads (code 6 and 5).  Many of the remaining
codewords correspond to transitions from one chord to another, \eg a
transition from a major triad to a minor triad in code 8.

(It is kind of interesting that sustained minor triad is more common
than the major triad (codes 4 and 5 in figure 7).  Don't fear the
reaper is in Amin, could it be related to this?)

Then, we use the LLE\footnote{implementation:
  \url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}}
algorithm \cite{Roweis2000} to visualize codewords arranged in
coherent groups (Figure \ref{fig:lle}).

>>>>

@@

\subsection{Pattern Creation}
Patterns are defined as a number of beats or bars. In the case of beats,
we simply cut the set of chromas per beat every $N$ beats. In the case
of bars, we gather all beats corresponding to the $N$ bars requested.
The number of chroma vectors we get can vary. We resize the features in the
time axis to a fixed length. Resizing instead of clipping can be argued over, 
but it should
preserve the main bar characteristics (such as a strong beat at the beginning
or a note change in the middle).

@@

\subsection{Codebook}
Visualizing codewords in a meaningful way is always a challenge, 
even if we have only a one or two hundreds of them.
We present $3$ figures in this section that should help the reader
foster his intuition. First, we display the most used codewords in
the testing set (Figure \ref{fig:codes1}). Then, we use the
 LLE\footnote{implementation: 
\url{http://www.astro.washington.edu/users/vanderplas/coding/LLE/}} 
algorithm \cite{Roweis2000} to visualize codewords arranged in
coherent groups (Figure \ref{fig:lle}).
